### 2011-06-15 standing-patches-paper.tex
/* Paper */ note about characteristic length
/* The Next Paper */

@@

Include stuff from ``comparison to panmixia'' here.

>>>>

XXX could do calculations as in "panmixia" here, e.g. if $f = (\chi/\sqrt{\pi \lambda_0})^2$ then
$f = 1-\gamma f^{3/2}$, where
$\gamma = (4 \pi^{5/2} / \sqrt{2}) \mu^2 s_b^{3/2} \rho^2 / \sigma \log(1/(1-s_d))$.
Then if $\gamma \ll 1$, $f \approx 1$, while if $\gamma \gg 1$, then $f \approx 0$.

@@

Include stuff from ``comparison to panmixia'' here:

Note that we are not considering the time it takes the mutation to fix locally.  
How long is this time?  Mean, variance.
When would we expect more mutations in this time?
Roughly, if populations are larger than $C/\mu$ for some $C \approx 100$.

Since we don't take this into account... we can ad-hoc it in by using the standing variation calculations -- add this to $\lambda_0$.
This is equivalent to changing $s_d$ by... how much?

Compare to panmixia: increases degree of parallel mutation if... ?
